Shannon diversity

### 2021-02-24 analysis/reports/table_1.Rmd
add HY figure and text edits. add algo from ha0ye/feasiblesads, rerendered to match formatting. renumber supplement files, note that they are NOT CORRECTLY NUMBERED in the reports directory but ARE CORRECT in manuscript/Supp

# Table S4

@@

overall_skew_results <- all_di %>%
  filter(s0 > 2, skew_unique > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(Dataset) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results <- all_di %>%
  filter(simpson_unique > 20) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(Dataset) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

>>>>

# Table 1

@@

overall_skew_results <- all_di %>%
  filter(s0 > 2, nparts > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(Dataset) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results <- all_di %>%
  filter(nparts > 20) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(Dataset) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

### 2021-02-24 analysis/rev_prototyping/old/shannon.Rmd

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

@@

ggplot(all_di, aes(s0, n0, color = shannon_cat)) +
  theme_bw()+
  scale_x_log10() +
  scale_y_log10() +
  scale_color_viridis_d(begin = .7) +
  geom_point(data = filter(all_di, is.na(shannon_cat)), aes(s0, n0), inherit.aes = F, alpha = .1, color = "grey") +
    geom_point(alpha = .5)+
  facet_wrap(vars(Dataset))
```

>>>>

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)

@@

ggplot(all_di, aes(s0, n0, color = shannon_cat)) +
  theme_bw()+
  scale_x_log10() +
  scale_y_log10() +
  scale_color_viridis_d(begin = .7) +
  geom_point(data = filter(all_di, is.na(shannon_cat)), aes(s0, n0), inherit.aes = F, alpha = .1, color = "grey") +
    geom_point(alpha = .5)+
  facet_wrap(vars(Dataset))

ggplot(all_di, aes(n0/s0, shannon_percentile, color = shannon_cat)) +
  theme_bw()+
  scale_x_log10() +
    geom_point()+
  facet_wrap(vars(Dataset), scales = "free")
```
